---
title: "the global COVID-19 epidemic situation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{the global COVID-19 epidemic situation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(COVIDsen)
```


This package provides the **covid** dataset, which contains the COVID-19 epidemic situation in 215 countries. The package also help you to launch the shiny app for you to know the situation of daily cases in the world. 

## How to launch the app 

You can install the released version of COVIDsen from [GitHub](https://github.com/etc5523-2020/r-package-assessment-Sen101) with:


``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-Sen101")
```
After that you could launch the app from the `COVIDsen` package with:

```{r, eval=FALSE}
launch_app()
```

## Instructions

The purpose of the app is to let people can clearly understand the COVID-19 situation.

These packages are needed to be installed when you run the APP:
-tidyverse

-shiny

-plotly

-leaflet

-ggplot2

-DT

The first part is the covid-19 situation in different countries and users can select the different countries to know the different cases trend by date.

The second part is the global map about the covid-19 cases and users can select the date and type to know the different situations in the world.

The third part is the table and users can search any country and state data in the table.





